\documentclass[9pt,letterpaper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

\definecolor{accent}{HTML}{2F5597}
\hypersetup{colorlinks=true,urlcolor=accent,linkcolor=accent}
\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}
\titlespacing*{\section}{0pt}{0.5em}{0.2em}
\setlength{\parskip}{0pt}
\setlist[itemize]{leftmargin=*, itemsep=1pt, topsep=1pt}

\begin{document}
\thispagestyle{empty}

{\Huge\bfseries Diego Gerardo Sánchez Moreno}\\
\small Querétaro, Mexico \\
\small Email: \href{mailto:diegogerardosanchez3@gmail.com}{diegogerardosanchez3@gmail.com} \;|\; Phone: +52 446 138 5307\\
\small LinkedIn: \href{https://www.linkedin.com/in/diego-gerardo-sánchez-moreno-73549a296}{diego-gerardo-sánchez-moreno-73549a296}\\
\small GitHub: \href{https://github.com/DiegoSanMo6011}{github.com/DiegoSanMo6011}\\
\small Portfolio: \href{https://diegogerardo.com}{diegogerardo.com}

\section*{Summary}
Robotics and embedded systems engineer in training focused on control, perception, and real‑world deployments. Seeking software/robotics roles where control, embedded systems, and applied perception are core.

\section*{Education}
\textbf{B.S. in Robotics and Digital Systems Engineering}\\
Tecnológico de Monterrey, Campus Querétaro\\
2022 -- Jun 2026 (expected)

\section*{Experience / Research}
\textbf{Hybrid Soft Robotics Lab, Tec de Monterrey (Querétaro) — Soft Robotics Control Platform}\\
\textit{2024 -- Present}
\begin{itemize}[leftmargin=*]
  \item Designed a bi‑stable pneumatic driver with closed‑loop pressure/vacuum control and safety interlocks.
  \item Implemented micro‑ROS on ESP32 (UART) with pressure sensing via I2C (ADS1115).
  \item Built Python SDK + GUI for reproducible experiments and logging; analyzed control data with MATLAB.
  \item Developed locomotion experiment workflows and a scalable architecture for ongoing research.
\end{itemize}

\textbf{Patio Cinco (Querétaro) — Production Platform}\\
\textit{2025 -- 2026}
\begin{itemize}[leftmargin=*]
  \item Delivered a production system for memberships, billing, and customer operations used by real clients.
  \item Implemented modular flows on Wix + Velo with relational backend and operational logging.
\end{itemize}

\textbf{Barbacoa de Miranda (Querétaro) — POS System}\\
\textit{2025 -- 2026}
\begin{itemize}[leftmargin=*]
  \item Built an offline‑first POS for Raspberry Pi with local queueing (SQLite) and auto‑sync to backend.
\end{itemize}

\section*{Selected Projects}
\textbf{PuzzleBot Autonomous Mobile Robot (ROS 2)}\\
\textit{Jan–Jun 2025}
\begin{itemize}[leftmargin=*]
  \item Integrated micro‑ROS, encoder‑based odometry, and YOLOv8 perception on Jetson Nano.
  \item Implemented telemetric distance tracking and validated autonomous motion.
\end{itemize}

\textbf{Line-Maze Solver (Pololu 3pi+)}\\
\textit{2024}
\begin{itemize}[leftmargin=*]
  \item Implemented PID line following with route recording and simplification to optimize traversal.
\end{itemize}

\section*{Awards \& Certifications}
\begin{itemize}[leftmargin=*]
  \item Best Poster Award — Exploring Soft Robotics (Dec 2025)
  \item NVIDIA DLI: Fundamentals of Deep Learning (Jun 2025)
  \item OpenCV Bootcamp (Apr 2025)
  \item Google Cloud Computing Fundamentals (Mar 21, 2023)
\end{itemize}

\section*{Technical Skills}
\begin{itemize}[leftmargin=*]
  \item \textbf{Languages:} C++, Python, TypeScript, VHDL, MATLAB
  \item \textbf{Robotics/Control:} ROS 2 (Humble), micro-ROS, PID/PI, odometry, Gazebo
  \item \textbf{Perception:} OpenCV, YOLOv8
  \item \textbf{Hardware:} ESP32, Jetson Nano, Raspberry Pi, Arduino, FPGA
  \item \textbf{Product/Web:} Wix + Velo, Supabase, PostgreSQL, Astro, Tailwind
\end{itemize}

\section*{Languages}
Spanish (Native), English (B2)

\end{document}
