\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

\definecolor{accent}{HTML}{2F5597}
\hypersetup{colorlinks=true,urlcolor=accent,linkcolor=accent}
\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}
\titlespacing*{\section}{0pt}{0.6em}{0.3em}

\begin{document}
\thispagestyle{empty}

{\Huge\bfseries Diego Gerardo Sánchez Moreno}\\
\small Software/Product Engineer (in training)\\
\small Querétaro, Mexico \\ 
\small Email: \href{mailto:diegogerardosanchez3@gmail.com}{diegogerardosanchez3@gmail.com} \;|\; Phone: +52 446 138 5307\\
\small LinkedIn: \href{https://www.linkedin.com/in/diego-gerardo-sánchez-moreno-73549a296}{diego-gerardo-sánchez-moreno-73549a296} \;|\; GitHub: \href{https://github.com/DiegoSanMo6011}{DiegoSanMo6011}\\
\small Portfolio: \href{https://diegogerardo.com}{diegogerardo.com}

\section*{Summary}
Software and product-oriented engineer in training with hands-on experience delivering production systems. Built operational platforms for real businesses with billing, memberships, and offline-first POS workflows. Seeking software/product roles with strong systems integration and reliability requirements.

\section*{Education}
\textbf{B.S. in Robotics and Digital Systems Engineering}\\
Tecnológico de Monterrey, Campus Querétaro\\
2022 -- Jun 2026 (expected)

\section*{Experience}
\textbf{Patio Cinco (Querétaro) — Production Platform}\\
\textit{Product/Systems Engineer | 2025 -- 2026}
\begin{itemize}[leftmargin=*]
  \item Delivered a production system for memberships, billing, and customer operations with persistent fiscal data.
  \item Migrated a basic Wix + Google Sheets workflow into a structured, traceable platform.
  \item Built modular flows on Wix + Velo backed by relational data and operational logging.
\end{itemize}

\textbf{Barbacoa de Miranda (Querétaro) — POS System}\\
\textit{Product/Systems Engineer | 2025 -- 2026}
\begin{itemize}[leftmargin=*]
  \item Built an offline-first POS for Raspberry Pi with local queueing (SQLite) and auto-sync to backend.
  \item Implemented a full-screen UI for fast cashier workflows and daily reporting.
\end{itemize}

\textbf{Hybrid Soft Robotics Lab (Tec de Monterrey, Qro.)}\\
\textit{Engineering Research | 2024 -- Present}
\begin{itemize}[leftmargin=*]
  \item Built a telemetry and control platform with a Python SDK + GUI and MATLAB-based analysis.
  \item Implemented embedded communication (ESP32 + micro-ROS) and data logging pipelines.
\end{itemize}

\section*{Selected Projects}
\textbf{Portfolio Website (Astro + Tailwind)}\\
\begin{itemize}[leftmargin=*]
  \item Designed a content-driven portfolio with reusable components and a clear technical narrative.
\end{itemize}

\textbf{PuzzleBot (ROS 2)}\\
\begin{itemize}[leftmargin=*]
  \item Integrated telemetry and perception pipeline in ROS 2 for autonomous driving demos.
\end{itemize}

\section*{Awards \& Certifications}
\begin{itemize}[leftmargin=*]
  \item NVIDIA DLI: Fundamentals of Deep Learning (Jun 2025)
  \item OpenCV Bootcamp (Apr 2025)
  \item Google Cloud Computing Fundamentals (Mar 21, 2023)
  \item Best Poster Award — Exploring Soft Robotics (Dec 2025)
\end{itemize}

\section*{Technical Skills}
\begin{itemize}[leftmargin=*]
  \item \textbf{Languages:} Python, TypeScript, C++
  \item \textbf{Backend/Data:} Supabase, PostgreSQL, SQLite, REST
  \item \textbf{Product/Web:} Wix + Velo, Astro, Tailwind
  \item \textbf{Systems:} Logging, offline queues, data sync, Raspberry Pi
\end{itemize}

\section*{Languages}
Spanish (Native), English (B2)

\end{document}
